Clean 2015 Raw Data

### 2018-04-25 data-raw/README.Rmd
Fix issue with numbers in N_management
Set to integer on creation

N_management <- tibble::tibble(
  `Nitrogen treatment` = character(),
  Year = integer(),
  `Total N (kg/ha)` = integer(),
  `Basal` = integer(),
  `Tillering` = integer(),
  `Panicle Initiation` = integer()
  )

@@

  N_management$Year <- c(2015,
  2015,
  2015,
  2016,
  2016)

  N_management$`Total N (kg/ha)` <- c(0,
  100,
  120,
  60,
  180)

  N_management$Basal <- c(0,
  60,
  60,
  30,
  60)

  N_management$Tillering <- c(0,
  20,
  30,
  30,
  60)

  N_management$`Panicle Initiation` <- c(0,
  20,
  30,
  0,
  60)

>>>>

N_management <- tibble::tibble(`Nitrogen treatment` = character())

@@

N_management$Year <- as.integer(c(2015,
                                  2015,
                                  2015,
                                  2016,
                                  2016))

N_management$`Total N (kg/ha)` <- as.integer(c(0,
                                               100,
                                               120,
                                               60,
                                               180))

N_management$Basal <- as.integer(c(0,
                                   60,
                                   60,
                                   30,
                                   60))

N_management$Tillering <- as.integer(c(0,
                                       20,
                                       30,
                                       30,
                                       60))

N_management$`Panicle Initiation` <- as.integer(c(0,
                                                  20,
                                                  30,
                                                  0,
                                                  60))
